---
title: "Session 10 - Time-Series Cross-Sectional Analysis"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: false
    css: "css/learnr-theme.css"
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(learnrhash)
library(texreg)
library(qmir22dw)
gradethis:: gradethis_setup()

library(tidyverse)

#load("./data_raw/df_learnr12.rda")
df_tscs <- df_learnr12
usethis::use_data(df_tscs, internal = F, overwrite = TRUE)

#load("df_learnr12.rda") # for local testing
```


## Introduction

Welcome to this week's learnr-exercises! In today's tutorial you will run a pooled model, a fixed-effects model, compare the results, and predict values for Japan and Uruguay! Before we start modeling, though, let's repeat some key contents of the lecture. 

```{r q1, echo = FALSE}
question("Why does it make sense to use a TSCS model?",
  answer("To adress concerns about omitted variable bias", correct = T),
  answer("To account for potential exogenous shocks", correct = T),
  answer("To deal with NAs in our data set"),
  answer("To incorporate unit-specific, time-varying characteristics in our model"),
  random_answer_order = F,
  allow_retry = T,
  incorrect = "Hint: You may want to check the lecture materials."
)
```

```{r q2, echo = FALSE}
question("What is commonly **not** constant within units over time?",
  answer("The electoral system", message = "How often has the electoral system in your home-country changed in your lifetime?"),
  answer("The unemployment rate", correct = T),
  answer("Culture", message = "Though you may argue that culture is everchanging and subject to the understanding of the individual, for an FE-regression we may assume that it is somewhat constant over time."),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Think about how much variation there is in each answer option."
)
```

```{r q3, echo = FALSE}
question("When may we want to use a two-way FE model?",
  answer("When we want to test two competing explanations", message = "We can do this with or without a fixed effect!"),
  answer("When we want to account for two variables that are constant over time", message = "Two variables that are constant over time, but differ from unit to unit would be covered with a unit-fixed effect."),
  answer("When we want to account for differences between units that are constant over time and for exogenous shocks that affect all units simultaneously", correct = T),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: You may want to check the lecture materials."
)
```

```{r q4, echo = FALSE}
question("What happens when we use a unit-fixed effect?",
  answer("It changes the intercept for each unit", correct = T),
  answer("It changes the slope for each unit"),
  answer("It runs a separate model for each unit"),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Check the lecture materials."
)
```


## Regression Exercises

Góméz-Díaz and Góméz-Díaz (2020) have argued that prolonged membership in the European Union leads to an increase in regional authority in different member-states. However, they also include a variable for the duration of World Bank membership. In the following, we will focus on the effect of World Bank membership on sub-national authority. In a final step we will calculate predicted values for Japan and Uruguay.

In the following exercises you will need these variables:

| Variable name |  Description
|:--------------|:-------------
| `n_RAI` | The dependent variable. Measures the regional authority
| `length_EU` |  Duration of EU membership in years
| `length_world` | Duration of World Bank membership in years
| `democ` | Polity2 democracy index
| `gdp_capita` | Gross domestic product per capita
| `population_size` | Size of population
| `nationalization` | Nationalization of the party system
| `country_name` | Name of the country


### Preparing the data and running our first model.


Let's take a look at our data `df_tscs`. In the first step, we want you to run a pooled model using the following variables: `n_RAI`, `length_EU`, `length_world`, `democ`, `gdp_capita`, `population_size`, and `nationalization`.


```{r exercise1, exercise = TRUE}
# Let's run our first model and call it pooled_model

```

```{r q5, echo = FALSE}
question_text("What is the coefficient for the duration of World Bank membership (`length_world`) in the pooled model? Round the coefficient to two digits after the decimal.",
  answer("-0.04", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Have you rounded correctly?"
)
```


Now run the same model, but include a fixed-effect for the unit. Our unit is the country (`country_name`)`. Let's call this model "fe_model".
```{r exercise2, exercise = TRUE}

```


```{r q6, echo = FALSE}
question_text(" What is the unit-specific intercept for Albania? Round the coefficient to two digits after the decimal.",
  answer("0.86", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: is the fixed-effect correctly specified?"
)
```

```{r q7, echo = FALSE}
question_text("What is the coefficient for the duration of World Bank membership  (`length_world`) in the fixed-effects model? Round the coefficient to two digits after the decimal.",
  answer("0.03", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: is the fixed-effect correctly specified?"
)
```



```{r q8, echo = FALSE}
question_text("If you wanted to present your results in a table using `screenreg()`, but wanted to exclude the country FE's from the table, what argument would you use?",
  answer("omit.coef", correct = T),
  answer("omit.coef = country_name", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Take a look at the arguments of the screenreg()-function."
)
```


```{r q9, echo = FALSE}
question("Comparing the coefficients from the pooled model and from the FE model, what do you conclude?",
         answer("Due to omitted variable bias our estimate we would have expected a negative relationship between the duration of World Bank membership. After accounting for the unobserved, constant variation between countries, we were able to show that the relationship is, in fact, positive and statistically significant.", correct = T),
         answer("Accounting for the unobserved, constant variation between countries has shown that there is no effect of World Bank membership on regional authority"),
         answer("We have different numbers of observation and therefore the coefficients differ.", message = "Take a look at the number of observations included in each model. Are they the same or do they differ?"),
         answer("The coefficients are the same.", message = "If the coefficients are the same, you may want to retrace your steps and check your code whether there is an error."),
         random_answer_order = TRUE,
         allow_retry = T
)
```

## Prediction

Remember from the last sessions that predicted values can help us to communicate the results of our analysis. In the following section, the model has already been specified. Please calculate predicted values and confidence intervals for the maximum duration of membership in the **World Bank** for Uruguay and Japan. Compare the predictions. In which of the two countries is the predicted value higher? Don't forget about the confidence intervals.




```{r exercise3, exercise = TRUE}
fe_model <-  lm(n_RAI ~ length_EU + length_world + democ + gdp_capita + population_size + nationalization + country_name-1, data = df_tscs)

```

```{r q10, echo = FALSE}
question("Comparing the predicted values, in which country is the prediction for sub-national authority higher?",
  answer("Japan", message = "Keep in mind that confidence intervals are important!"),
  answer("Uruguay", message = "Keep in mind that confidence intervals are important!"),
  answer("Unclear, because the confidence intervals overlap.", correct = T),
  random_answer_order = TRUE,
  allow_retry = T)
```

In a final step, we want you to calculate predicted values for minimum and maximum values of World Bank membership for Japan and compare them.


```{r exercise4, exercise = TRUE}


```

```{r q11, echo = FALSE}
question_text("What is the difference in predicted values for minimum and maximum World Bank membership for Japan? Round to two digits after the decimal",
  answer("2.10", correct = T),
  answer("2.1", correct = T),
  allow_retry = T,
  incorrect = "Did you correctly specify the scenarios?")
```



## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(default_ui(url = "https://ilias.uni-mannheim.de/goto.php?target=svy_1239770&client_id=ILIAS"))
```