---
title: "Session 11 - Causal Inference"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: false
    css: "css/learnr-theme.css"
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(learnrhash)
library(tidyverse)
library(highlight)
library(gradethis)

gradethis::gradethis_setup()
data(df_learnr14)

load("./data_raw/df_learnr14.rda")
df_ci <- df_learnr14
usethis::use_data(df_ci, internal = F, overwrite = TRUE)

```

## Introduction

Welcome back to the tutorial for week 14! It is the second to last tutorial and as always we will start with some knowledge questions to repeat the lecture. In the coding exercises, you will look at the support for the European Union among the citizens of member-states. Good luck and have fun!

## Knowledge Questions

```{r q1, echo = FALSE}
question("What is the general problem with causal inference for observational data?",
  answer("The observed difference in outcomes might be caused by confounders instead of the treatment.", correct = T),
  answer("The treatment does not work because of confounders.", message = "Think about the role of confounders in analyses of observational data. The treatment may work, but we do not know what influence the confounders have had!"),
  answer("Observational data does not tell us which unit is from the treatment and the control group."),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Check the lecture materials."
)
```

```{r q2, echo = FALSE}
question("What is the identification strategy for difference-in-differences designs?",
  answer("The treatment group`s change over time in absence of the treatment is equal to the control group`s change over time.", correct = T),
  answer("The outcome for the treatment group in absence of the treatment is identical to the outcome of the control group.", message = ""),
  answer("The average causal effect is the difference in the treatment group's outcome before and after the treatment.", message = "What role does the control group play here?"),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Check the lecture materials."
)
```

## Difference-in-Differences

Take a look at our data-set `df_learnr14`. What is the average degree of anti-authoritarianism (`cntrymean_antiauth`) among EU members(`EU`) in 2008-2010 (`wave`). Please round to the second decimal.

```{r exercise1, exercise = TRUE}

```

```{r q3, echo = FALSE}
question_text("What is the average degree of anti-authoritarianism among EU members in 2008-2010 ('cntrymean_antiauth').",
  answer("75.69", correct = T),
  answer("75.7", correct = T),
  answer("75.70", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Select the relevant observations with 'filter()' and use the 'mean()' command to calculate the average."
)
```

```{r q4, echo = FALSE}
question_text("And what about the average degree of anti-authoritarianism among non-EU members in the same time frame?",
  answer("67.2", correct = T),
  answer("67.18", correct = T),
  answer("67.20", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Select the relevant observations with \"filter()\" and use the \"mean()\" command to calculate the average."

)
```

In the next few tasks, you will go through the steps necessary to calculate the causal effect of EU membership on the anti-authoritarian attitudes of the countries` citizens using a difference-in-differences design. In particular, you will calculate the causal effect of EU-accession on anti-authoritarian values for Romania (treatment unit) compared to Albania (control unit) assuming that anti-authoritarian attitudes would have developed similarly in both countries in the absence of Romania's EU accession.

Calculate the change in anti-authoritarian values for Romania between 2008-2010 and 1999-2004. Round to two digits after the decimal. 


```{r exercise2, exercise = TRUE}

```

```{r q5, echo = FALSE}
question_text("What is the change in anti-authoritarian values for Romania between 2008-2010 and 1999-2004. Round to two digits after the comma.",
 # answer(0.32, correct = T),
  answer("0.32", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Following what we have done in the lab, calculate the values of \"cntrymean_antiauth\" for Romania for these two time points and subtract them from each other."
)
```

Now, calculate the change in anti-authoritarian values for Albania between 2008-2010 and 1999-2004. Round to two digits after the comma.

```{r exercise3, exercise = TRUE}

```

```{r q6, echo = FALSE}
question_text(
  "What is the change in anti-authoritarian values for Albania between 2008-2010 and 1999-2004. Round to two digits after the comma.",
 # answer(-4.77, correct = T),
  answer("-4.77", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Following what we have done in the lab, calculate the values of \"cntrymean_antiauth\" for Albania for these two time points and subtract them from each other."
)
```


## Calculating the ATE

What is the average treatment effect of EU accession for Romania? Based on the two previous exercises you already have everything you need! Alternatively, you can use the code below to calculate the difference between waves (`difference_within`) for the two countries. They will be stored in two objects (`albania`and `romania`). Do not forget to round to two digits after the comma.

```{r set-up}


albania <- df_learnr14 %>% 
    # select relevant variables
  select(countryname, wave, cntrymean_antiauth) %>% 
  # filter for treatment and control cases
  filter(countryname == "Albania") %>% 
  # filter for pre and post treatment period
  filter(wave == "1999-2004" | wave == "2008-2010") %>% 
  # spread out the year variable to make calculation easier
  spread(wave, cntrymean_antiauth) %>%
    # rename year values
  rename("wave2" = `2008-2010`,
         "wave1" = `1999-2004`) %>%
  # Calculate difference within units
  mutate(difference_within = wave2 - wave1)



romania <- df_learnr14 %>% 
    # select relevant variables
  select(countryname, wave, cntrymean_antiauth) %>% 
  # filter for treatment and control cases
  filter(countryname == "Romania") %>% 
  # filter for pre and post treatment period
  filter(wave == "1999-2004" | wave == "2008-2010") %>% 
  # spread out the year variable to make calculation easier
  spread(wave, cntrymean_antiauth) %>%
    # rename year values
  rename("wave2" = `2008-2010`,
         "wave1" = `1999-2004`) %>%
  # Calculate difference within units
  mutate(difference_within = wave2 - wave1)

```

```{r exercise4, exercise = TRUE}


```

```{r q8, echo = FALSE}
question_text(
  "What is the average treatment effect of EU accession for Romania? Round to two digits after the comma.",
#  answer(5.09, correct = T),
  answer("5.09", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: The average treatment effect for the treated (in this case, Romania) is the difference between the change in outcomes for the treatment unit (Romania) and the change in outcomes for the control unit (Albania)."
)
```


```{r q9, echo = FALSE}
question("Does this mean that anti-authoritarian attitudes in Romania ... due to EU accession?",
  answer("increased", correct = T),
  answer("decreased"),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Think about what the treatment effect means."
)
```

## Regression Difference-in-Differences

In a final step, we want you to analyze a difference-in-differences regression model. The treatment group and treatment time are already specified for you in the next chunk. 


```{r exercise5, exercise = TRUE}

did_data <- df_learnr14 %>% tibble() %>%
  filter(countryname == "Romania" | countryname == "Albania" | countryname == "Finland" | countryname == "Ukraine" | countryname == "Switzerland") %>%
  mutate(treatment_time = ifelse(wave == "2008-2010", 1, 0),
         treatment_group = ifelse(countryname == "Romania", 1, 0))

```

```{r q10, echo = FALSE}
question_text(
  "What is the average treatment effect of EU accession in the regression model? Please round to two digits after the decimal",
  answer("-8.23", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint:Have you specified the data correctly?"
)
```




## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(default_ui(url =""))
```