---
title: "Session 12- Logistic Regression"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: false
    css: "css/learnr-theme.css"
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(learnrhash)
library(tidyverse)
library(highlight)
library(gradethis)
library(texreg)

gradethis::gradethis_setup()

load("./data_raw/df_learnr15.rda")
df_logistic <- df_learnr15
usethis::use_data(df_logistic, internal = F, overwrite = TRUE)

```

## Introduction

Welcome to the last tutorial of the Quantitative Methods in International Relations course! Today we will replicate some of the results of Sarah Hobolt\'s (2016) paper: \"The Brexit vote: a divided nation, a divided continent\". We will use different survey items to test hypotheses about the decision to vote "Leave" in the Brexit referendum. These variables are **categorical**, except for the `age`-variable which is numeric. 

As always, we will start with some knowledge questions and then continue with some coding exercises. Have fun!



## Knowledge Questions

```{r q1, echo = FALSE}
question("Why is it useful to rely on logistic regression models for our referendum vote variable?",
  answer("Because our dependent variable is binary and our predicted values may fall outside the logical boundaries of 0 and 1 if we use OLS.", correct = T),
  answer("Because the variance of our dependent variable is not large enough."),
  answer("Because we cannot calculate a mean for our dependent variable."),
  answer("Because the standard deviation of our dependent variable equals its mean."),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Remember what we use OLS for and what our regression line would predict for different kinds of variables."
)
```

```{r q2, echo = FALSE}
question("Why do we need a link function for logistic regression analyses?",
  answer("Because we want to predict probabilities that only range between 0 and 1.", correct = T),
  answer("Because the variance needs to be logged in order to obtain predictions."),
  answer("Because logistic regression models analyze the responses of people participating in surveys.", message = "They do sometimes, but that does not affect the need for a link-function."),
  answer("Because that makes the derivation of the maximum likelihood easier."),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Consider the special feature of dependent variables in logistic regressions."
)
```

## Coding Exercises

Now let us have a look at the Brexit referendum data again (the data is stored as `df_logistic`). We want to compare some characteristics of the participants in the survey. In a first step, we want you to calculate the average of men in the data set and the average age of women in the data set. Then subtract the average age of women from that of the men. What is the difference in their ages?




```{r exercise1, exercise = TRUE}

```

```{r q3, echo = FALSE}
question_text("What is the age difference between men and women? Please round to two decimals",
  answer("1.7", correct = T),
  answer("1.70", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Select the relevant observations with 'filter()' and use the 'mean()' command to calculate the average."
)
```
"
Now calculate the mean age of voters who intend to vote "leave" (`LeaveVote == 1`) and those who intend to vote "remain" (`LeaveVote == 0`).

```{r exercise2, exercise = TRUE}

```

```{r q4, echo = FALSE}
question_text("What is the age difference between leave and remain voters? Please round to two decimals.",
  answer("8.38", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Select the relevant observations with `filter()` and use the `median()` command to calculate the median."
)
```

Now calculate a logit regression trying to explain `LeaveVote` with `age`, `female`, `edlevel`, `hhincome`, `EuropeanIdentity`, `EnglishIdentity` and `BritishIdentity`. Use the `glm()` command and don't forget to specify the link function. What is the coefficient for `EuropeanIdentity`? Round to two decimals.

```{r exercise3, exercise = TRUE}

```

```{r q5, echo = FALSE}
question_text("What is the coefficient for `EuropeanIdentity`? Rond to two decimals.",
  answer("-0.80", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Consider what we did in the lab. The regression command is similar, just add the new independent variables and don't include some that we do not use anymore."
)
```

```{r q6, echo = FALSE}
question("What does the coefficient for `EuropeanIdentity` tell us?",
  answer("That there is a negative relationship with voting Leave", correct = T),
  answer("That there is a positive relationship with voting Leave"),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Consider the lecture material and what you know about the signs of coefficients."
)
```

## Prediction

Now, let\'s calculate predicted probabilities. You can use the model below!
```{r , eval = F, echo }
model <- glm(LeaveVote ~ age + female + edlevel + hhincome + EuropeanIdentity +
               EnglishIdentity + BritishIdentity,
             data = df_logistic,
             family = binomial(link = "logit")) 
```

Calculate the predicted probability and the surrounding uncertainties of voting `Leave` for individuals with the highest value for `EuropeanIdentity`, holding all other variables at their means or medians. Remember, that the variables (apart from the `age`-variable) are questionnaire variables. Though they are numeric, the answer options have been categorical. What is the predicted probability to vote `Leave` for such voters? Round to two decimals.


```{r exercise4, exercise = TRUE}

```

```{r q7, echo = FALSE}
question_text("  What is the predicted probability to vote `Leave` for such voters? Round to two decimals.",
  answer("0.06", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Start with the lab code and extend the scenarios to the new variables we included. In case you received a prediction of 0.049/0.05, make sure that you set the questionnaire items to their medians."
)
```

Now, calculate predicted probabilities and the surrounding uncertainties, this time for the lowest value of `EuropeanIdentity`, holding everything else at its means or medians. What is the predicted probability for those individuals? Again, round to two decimals.

```{r exercise5, exercise = TRUE}

```

```{r q8, echo = FALSE}
question_text("What is the predicted probability for those individuals? Again, round to two decimals.",
  answer("0.88", correct = T),
  allow_retry = TRUE,
  incorrect = "Hint: Same as before, only the value for `EuropeanIdentity` has to be changed. In case you received a prediction of 0.86, make sure that you set the questionnaire items to their medians."
)
```

```{r q9, echo = FALSE}
question("What do these predictions tell you?",
  answer("People who identify with Europe a lot have a lower probability of voting Leave than those who do not, holding everything else at their respective mean or median.", correct = T),
  answer("People who identify with Europe a lot have a lower probability of voting Leave than those who do not."),
  answer("We cannot say anything about the relationship between high and low identification with Europe and voting Leave because the difference is not statistically significant."),
  answer("People who identify with Europe a lot have a higher probability of voting Leave than those who do not."),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Compare the predicted probabilities and the uncertainty around them."
)
```

## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(default_ui(url = ))
```